Predicting solutions for the Military Flight and Maintenance Planning problem

### 2020-09-09 R/presentations/EDAA202003/presentation.Rmd
last changes to ppt EDAA.

1. Train a statistical model to predict certain characteristics of good (optimal?) solutions for 5000 simulated instances.
2. Use this information to *predict* the characteristics of good solutions on a new instance ($\hat{\mu}_{t'-t}^{lb}$,  $\hat{\mu}_{t'-t}^{ub}$).
3. Apply the prediction to *guide* de solution of said instance.

>>>>

1. Train a statistical model to predict certain characteristics of good (optimal?) solutions for 5000 simulated scenario.
2. Use this information to *predict* the characteristics of good solutions on a new scenario: $\hat{\mu}_{t'-t}^{lb}$,  $\hat{\mu}_{t'-t}^{ub}$.
3. Apply the prediction to *guide* de solution of said scenario.
